---
title: "p8105_hw6_sl4662"
author: "Siying Li "
date: "11/18/2019"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(mgcv)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```

# Problem 1

## Data Cleaning

```{r}
birth_data = read.csv("./data/birthweight.csv")

check_class = lapply(birth_data, class)

birth_data = 
  birth_data %>% 
  mutate(
    babysex = factor(babysex, levels = c("1","2")),
    babysex = fct_recode(babysex, 
                           "male" = "1", 
                           "female" = "2"),
    frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9")),
    frace = fct_recode(frace, 
                         "white" = "1", 
                         "black" = "2",
                         "asian" = "3",
                         "puerto_rican" = "4",
                         "other" = "8",
                         "unknown" = "9"),
    malform = factor(malform, levels = c("1","0")),
    malform = fct_recode(malform, 
                         "absent" = "0", 
                         "present" = "1"),
    mrace = factor(mrace, levels = c("1", "2", "3", "4", "8")),
    mrace = fct_recode(mrace, 
                         "white" = "1", 
                         "black" = "2",
                         "asian" = "3",
                         "puerto_rican" = "4",
                         "other" = "8"),
    id = 1:4342,
         )
```


## Build my model 

```{r}
birth_data %>% 
  ggplot(aes(x = blength, y = bwt)) + 
  geom_point() + theme_bw()

birth_data %>% 
  ggplot(aes(x = bhead, y = bwt)) + 
  geom_point() + theme_bw()

birth_data = 
  birth_data %>% 
  mutate(
    babysex = fct_infreq(babysex),
    frace = fct_infreq(frace),
    malform = fct_infreq(malform),
    mrace = fct_infreq(mrace),
    )

# Backward elimination:
everything_fit = lm(formula = bwt ~ . -id, data = birth_data) 
summary(everything_fit)
# No NAs (pnumlbw, wtgain, pnumsga)
step1<-update(everything_fit, . ~ . -pnumlbw -wtgain -pnumsga)
summary(step1)
# No momage
step2<-update(step1, . ~ . -momage)
summary(step2)
# No ppbmi
step3<-update(step2, . ~ . -ppbmi)
summary(step3)
# No frace
step4<-update(step3, . ~ . -frace)
summary(step4)
# No malform
step5<-update(step4, . ~ . -malform)
summary(step5)
# No fincome
step6<-update(step5, . ~ . -fincome)
summary(step6)
# No menarche
mymodel<-update(step6, . ~ . -menarche)
summary(mymodel)
```

### Use method of backward elimination learned in Biostatistics class, which takes out non-significant variables 'one at a time', starting with the highest p-value. Conclusion is that predictors are: `babysex`, `bhead`, `blength`, `delwt`, `gaweeks`, `mheight`, `mrace`, `parity`, `ppwt`, `smoken`.

```{r}
prediction_residual = 
  birth_data %>% 
  add_predictions(mymodel) %>% 
  add_residuals(mymodel)

prediction_residual %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(color = "purple", alpha = 0.5, size = 0.5) +
  geom_smooth(method = "lm") +
  labs(x = "Predicted/Fitted Value",
       y = "Residual", 
       title = "Residual Plot")
```

### As shown in the plot, residues has a random pattern and evenly distrubuted around 0. 


## Compare with model: 

### 1: using length at birth and gestational age as predictors (main effects only)

### 2: using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model1 = lm(formula = bwt ~ blength + gaweeks, data = birth_data) 
summary(model1)

model2 = lm(formula = bwt ~ bhead*blength*babysex, data = birth_data) 
summary(model2)

```

### Cross Validation
```{r}
cv_df =
  crossv_mc(birth_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(mymodel = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
         model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model2 = map(train, ~gam(bwt ~ bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_mymodel = map2_dbl(mymodel, test, ~rmse(model = .x, data = .y)),
         rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = date)) + 
  geom_point() 


result = 
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    rsquare = map(models, broom::glance)) %>% 
  select(.id, results, rsquare) %>% 
  unnest(results, rsquare)

result %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(x = estimate)) + geom_density()

r.squared = 
  result %>% 
  select(.id, term, estimate, r.squared) %>% 
  group_by(.id) %>% 
  summarize(mean_r.squared = mean(r.squared)) 

r = 
  r.squared %>% 
  ggplot(aes(x = mean_r.squared)) + geom_density()


beta0 = 
  result %>% 
  select(.id, term, estimate, r.squared) %>% 
  group_by(.id) %>% 
  filter(term == "(Intercept)") %>% 
  summarize(beta0 = estimate)

beta1 = 
  result %>% 
  select(.id, term, estimate, r.squared) %>% 
  group_by(.id) %>% 
  filter(term == "tmin") %>% 
  summarize(beta1 = estimate)

 log_beta = 
  bind_cols(beta0, beta1) %>% 
  group_by(.id) %>% 
  summarize(log_beta = log(beta0 * beta1)) 
 
 beta_product = 
  log_beta %>% 
  ggplot(aes(x = log_beta)) + geom_density()
 
r + beta_product
```

```{r}
r_result = r.squared$mean_r.squared
quantile(r_result, c(.025, .975)) 

beta_result = log_beta$log_beta
quantile(beta_result, c(.025, .975)) 
```

### 95% confidence interval for r squared is :0.8936278 and 0.9274813. 

### 95% confidence interval for log(B1*B2) is :1.964565 and 2.057922. 